---
title: "MusicProjectPart2"
author: "Aaron Nicanor"
date: "11/14/2019"
output: html_document
---

Our goal with this assignment is to perform a multiple linear regression on the Music Insights data. First, I'll run the code I had made prior.
```{r}
suppressMessages(library("tidyverse"))
suppressMessages(library("knitr"))
suppressMessages(library("stringr"))
suppressMessages(library("caret"))
suppressMessages(library("dplyr"))
suppressMessages(purl("MusicProject.Rmd", output = "MusicProject.r"))
source("MusicProject.r")
```

I'll need to add some continuous data to the Person table. What I decided to do is add in the number of instruments that the person plays. The code below is me doing so.
```{r}
PersonModeling <- Person
#Change all empty repsonses to NA, and the one instance of a person saying "none" into an NA value as well.
PersonModeling$instrument_list[PersonModeling$instrument_list==""]<-NA
PersonModeling$instrument_list[PersonModeling$instrument_list=="None"]<-NA

#Anyone with NA as their response will have their instrument count set to 0, while everyone else who did submit a response must've played at least one instrument. I then add all the seperators within their responses and add it to their instrument count.
PersonModeling$instrument_count <- str_count(PersonModeling$instrument_list, ",") + 1
PersonModeling$instrument_count[is.na(PersonModeling$instrument_list)] <- 0
```

Here, I split the data into two tables: a train and test table.
```{r}
index <- createDataPartition(PersonModeling$instrument_count, p = 0.75, list = FALSE)
train <- PersonModeling[index, ]
test <- PersonModeling[-index, ]
```

Now, I test the predictors of my chosen dependant variable (in this case, it's instrument_count) to observe if there's any relation. My independant variables are academic_major, academic_level, year_born, and sex. Using the summary function, I can find which independant variable is likely to predict the instrument count of a person.
```{r}
train_model <- lm(train, formula = instrument_count ~ academic_major + academic_level + year_born + sex)
summary(train_model)
```
